---
title: "Data analysis"
author: "Sergey Kramp"
date: "4/4/2022"
output: html_document
---
## Loading the data and libraries

```{r, echo=FALSE}
library(data.table)
library(tidyverse)
library(stringr)
library(patchwork)

companies_DAX <- fread("C:/Users/Sergey Kramp/Documents/School Material/6_SS 2022/01_Thesis/Data/companies_Dax40.csv", encoding = "UTF-8")
members_DAX <- fread("C:/Users/Sergey Kramp/Documents/School Material/6_SS 2022/01_Thesis/Data/members_Dax40.csv", encoding = "UTF-8")
companies_MDAX <- fread("C:/Users/Sergey Kramp/Documents/School Material/6_SS 2022/01_Thesis/Data/Companies_MDax.csv")
members_MDAX <- fread("C:/Users/Sergey Kramp/Documents/School Material/6_SS 2022/01_Thesis/Data/Members_MDax.csv", encoding = "UTF-8")

```

## Preparing the data
```{r}

companies_DAX[, Index := "DAX"]
companies_MDAX[, Index := "MDAX"]
# combine DAX and MDAX
members <- rbind(members_DAX, members_MDAX)
companies <- rbind(companies_DAX, companies_MDAX)

prepare_member_data <-function(members) {
members <- members[!duplicated(Name)]
names(members) <- gsub(x = names(members), " ", "_")
members[, Age:= 2022- `Year_of_Birth`]
members[, Tenure:= 2022 - `Member_Since`]
members[, ':='(CV = NULL, `Year_of_Birth` = NULL, `Member_Since` = NULL)]
members[Gender == "M", Gender := "Male"]
members[Gender == "F", Gender := "Female"]
members[Sustainability_experience == "Y", Sustainability_experience := "Yes"]
members[Sustainability_experience == "N", Sustainability_experience := "No"]
members[PhD == "Y", PhD := "Yes"]
members[PhD == "N", PhD := "No"]
members[`Post-Doc` == "Y", `Post-Doc` := "Yes"]
members[`Post-Doc` == "N", `Post-Doc` := "No"]
members[Employee_Delegat == "Y", Employee_Delegat := "Yes"]
members[Employee_Delegat == "N", Employee_Delegat := "No"]
members[,':='(Nationality = as.factor(Nationality), Gender = as.factor(Gender), PhD = as.factor(PhD), `Post-Doc` = as.factor(`Post-Doc`),
              `Employee_Delegat` = as.factor(`Employee_Delegat`), `Sustainability_experience` = as.factor(`Sustainability_experience`))]
members[PhD == "", PhD := NA]
members[`Post-Doc` == "", `Post-Doc` := NA]
members[`Employee_Delegat` == "", `Employee_Delegat` := NA]
members[`Sustainability_experience` == "", `Sustainability_experience` := NA]
members[Nationality == "", Nationality := NA]
members[, International := ifelse(Nationality == "German", "No", "Yes")][,International := as.factor(International)]
members[is.na(Nationality), International := NA]
members[, Committees := str_trim(Committees)]
members <- separate(members, col = "Committees", into = c("Committee_1", "Committee_2", "Committee_3", "Committee_4", "Committee_5", "Committee_6", "Committee_7"), sep = ",")
return(members)
}

members_DAX <- prepare_member_data(members_DAX)
members_MDAX <- prepare_member_data(members_MDAX)
members <- prepare_member_data(members)

prepare_company_data <- function(companies){
names(companies) <- gsub(x = names(companies), " ", "_")
companies[,':='(`Sustainability_Experience` = as.factor(Sustainability_Experience))]
companies[, Sustainability_Committee := ifelse(grepl("Sustainability Committee",Tags), 1, 0)]
companies[, Alleged_Expert := ifelse(grepl("Alleged Expert",Tags), 1, 0)]
companies[, Sustainability_Expert := ifelse(grepl("Sustainability Expert",Tags), 1, 0)]
companies[, Trainning := ifelse(grepl("Trainning",Tags), 1, 0)]
companies[, Task_of_existing_committee := ifelse(grepl("Task of existing committee",Tags), 1, 0)]
companies[, Tags := NULL]
companies[, Industry := str_trim(Industry)]
companies[, Index := as.factor(Index)]

return(companies)
}

companies_DAX <- prepare_company_data(companies_DAX)
companies_MDAX <- prepare_company_data(companies_MDAX)
companies <- prepare_company_data(companies)
```


## Set default theme
```{r}
theme_set(theme_minimal())
windowsFonts(A = windowsFont("Times New Roman"))
theme_update(text = element_text(size=14,  family= "A"))
```

## General information about the sample
```{r}
# Gender
ggplot(members, aes(x = Gender)) + geom_bar() + geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, position = position_dodge(2)) + labs(title = "Most supervisory board members are male")
```



## General with and without experience - members
```{r, include=TRUE}
ggplot(members[!is.na(Sustainability_experience)], aes(Sustainability_experience, fill = Sustainability_experience)) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) + ylab("Number of board members") + xlab("Has sustainability experience?") + scale_fill_manual(values = c("#fa766e", "#00bf7d")) + theme(legend.position = "none")

```


## General with and without experience - companies
```{r, echo=T}
ggplot(companies, aes(x= Sustainability_Experience, fill = Sustainability_Experience)) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) + ylab("Number of supervisory boards") + xlab("Has sustainability experience?") + scale_fill_manual(values = c("#fa766e", "#00bf7d")) + theme(legend.position = "none")
  #labs(title = "Majority of companies don't have sustainability experience")
```

## General with and without experience - companies (DAX)
```{r, echo=T}
DAX <-  ggplot(companies_DAX, aes(x= Sustainability_Experience, fill = Sustainability_Experience )) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) +
  labs(title = "DAX") + ylab("Number of supervisory boards") + ylim(0,30) + xlab("Has sustainability experience?") + scale_fill_manual(values = c("#fa766e", "#00bf7d")) + theme(legend.position = "none")

```

## General with and without experience - companies (MDAX)
```{r, echo=T}
MDAX <- ggplot(companies_MDAX, aes(x= Sustainability_Experience, fill = Sustainability_Experience)) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) +
  labs(title = "MDAX") + ylab("Number of supervisory boards") + ylim(0,30) + xlab("Has sustainability experience?") + scale_fill_manual(values = c("#fa766e", "#00bf7d")) + theme(legend.position = "none", axis.title.y = element_blank(), axis.ticks.y = element_blank())

```

## Comparsion of DAX and MDAX
```{r}
DAX + MDAX

```

## For sustinability experts
```{r}
experts <- members[!is.na(Sustainability_experience)][Sustainability_experience == "Yes"]
```

## Distrebution of men vs. women in general sample
```{r, echo=T}
ggplot(members[!is.na(Gender)], aes(x=Gender, fill = Gender)) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) + ylab("Count") + scale_fill_manual(values = c("#fa766e", "#07b4f4")) + theme(legend.position = "none") + labs(title = "General sample")
```

## Distribution of men vs women experts
```{r, echo=T}
ggplot(experts[!is.na(Gender)], aes(x=Gender, fill = Gender)) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) + ylab("Count") + scale_fill_manual(values = c("#fa766e", "#07b4f4")) + theme(legend.position = "none") + labs(title = "Board members with sustainability experience")
```

###  Binomial test to check Female vs. Male distribution
```{r}
# For p used the probablity of sampling a male from the general sample
p <- members[Gender == "Male", .N] / members[,.N]
pbinom(experts[Gender == "Male",.N],nrow(experts), lower.tail = T, prob = p)

# The probablity is 0.0007399314 which is lower than 0.05
```

## Age of members with and without sustainability experience
```{r, echo=T}
ggplot(members[!is.na(Age)], aes(y = Age, fill = Gender)) + geom_boxplot(position = position_dodge(1)) + facet_wrap(~Sustainability_experience, labeller = "label_both") + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_blank())

summary(members[, Age])
summary(members[Sustainability_experience == "Yes" ,Age])
summary(members[Sustainability_experience == "No" ,Age])

nrow(members[!is.na(Age)])
nrow(members[!is.na(Age) & Sustainability_experience == "Yes"])
nrow(members[!is.na(Age) & Sustainability_experience == "No"])

sd(members[, Age], na.rm = T)
sd(members[Sustainability_experience == "Yes" ,Age], na.rm = T)
sd(members[Sustainability_experience == "No" ,Age], na.rm = T)

t.test(Age ~ Sustainability_experience, data = members, alternative = "two.sided")
```
## T test to check if there is a difference
```{r}
t.test(Age~Gender, data = experts)
# test shows there is no difference
```

#PhD
```{r}
prop <- c (
  members_no_NA[Sustainability_experience == "No" & PhD == "No", .N] / members_no_NA[Sustainability_experience == "No",.N],
  members_no_NA[Sustainability_experience == "No" & PhD == "Yes", .N] / members_no_NA[Sustainability_experience == "No",.N],
  experts_no_NA[PhD == "No", .N] / experts_no_NA[, .N],
  experts_no_NA[PhD == "Yes", .N] / experts_no_NA[, .N]
)

SE <- c("No", "No", "Yes", "Yes")

phd <- c("No", "Yes", "No", "Yes")

dt_prop <- data.table(Proportion = prop, Sustainability_Experience = SE, PhD = phd)

ggplot(dt_prop, aes(x = Sustainability_Experience, fill = PhD, weight= Proportion)) + geom_bar() + labs(title = "There is no significant difference in proportion of PhDs") + ylab("Proportion") +
  xlab("Sustainability Experience")

q1 <- members_no_NA[Sustainability_experience == "No" & PhD == "Yes", .N]
q2 <- members_no_NA[Sustainability_experience == "Yes" & PhD == "Yes", .N]

n1 <- members_no_NA[Sustainability_experience == "No", .N]
n2 <- members_no_NA[Sustainability_experience == "Yes", .N]

p1 <- q1 / n1
p2 <- q2 / n2
p_pooled <- (q1 + q2) / (n1 + n2)

z <- (p1 - p2) / sqrt((p_pooled * (1 - p_pooled))/ n1 + (p_pooled * (1 - p_pooled))/n2)
p_value <- 2 * pnorm(z, lower.tail = T)

```

## Tenure of experts
```{r}
ggplot(experts[!is.na(Tenure)], aes(y = Tenure, fill = Gender)) + geom_boxplot(position = position_dodge(1)) +  labs(title = "Distribution of the tenure of sustainability experts by gender")
```


## Tenure of experts vs. non-experts

```{r}
ggplot(members, aes(y = Tenure, fill = Sustainability_experience)) + geom_boxplot(position = position_dodge(1)) + labs(title = "There is no significant difference in tenure based on experiance in sustainability")
t.test(Tenure ~ Sustainability_experience, data = members)

members[!is.na(Tenure), .N]
summary(members[!is.na(Tenure), Tenure])
members[!is.na(Tenure), sd(Tenure)]
members[!is.na(Tenure), sd(Tenure), by = Sustainability_experience]
members[!is.na(Tenure), mean(Tenure)]
members[!is.na(Tenure), summary(Tenure), by = Sustainability_experience]
members[!is.na(Tenure), .N, by = Sustainability_experience]


t.test(Tenure~Sustainability_experience, data = members[!is.na(Tenure)], alternative = "two.sided")
```

## Distribution of employee representative vs. shareholder representatives
```{r}
ggplot(members[!is.na(Employee_Delegat)], aes(x = Employee_Delegat)) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) + labs(title = "General sample") + ylab("Count") + xlab("Employee Representative")
```

## Distribution of employee representatives vs. shareholder representatives (among sustainability experts)
```{r}
ggplot(members[!is.na(Employee_Delegat) & `Sustainability_experience` == "Yes"], aes(x = Employee_Delegat)) + geom_bar() + geom_text(stat='count', aes(label=..count..),position = position_dodge(2), vjust=-0.5) + 
  labs(title = "Among board members with sustainability experience") + ylab("Count") + xlab("Employee Representative")
```

## Binomial test check Employee_Delegat distribution
```{r}
# p used was the probablity of sampling an Employee_Delegat from general sample

p <- members[Employee_Delegat == "Y", .N] / members[ ,.N]
pbinom(experts[Employee_Delegat == "Y", .N], nrow(experts), lower.tail = T, prob = p)

# The probability is 4.44998e-05 and therefore much lower than 0.05
```

## Board sizes of comapnies with and without sustainability expertise

```{r}
ggplot(companies, aes(y = Board_size, fill = Sustainability_Experience)) + geom_boxplot(position = position_dodge(1)) + ylab("Board Size") + labs(fill = "Sustainabiliy Experience", title = "There is no statistically significant difference in board size") + facet_wrap(~Index)
```

## Check if there is a real differnce with t test
```{r}
t.test(Board_size~Sustainability_Experience, data = companies, paired = F)
# The test reveals there is a significant difference in board sized

# Test for DAX companies
t.test(Board_size~Sustainability_Experience, data = companies_DAX, paired = F)

# Test for MDAX companies
t.test(Board_size~Sustainability_Experience, data = companies_MDAX, paired = F)

# The difference is confounded by the index
```


## International sustainability experts
```{r}
members_no_NA <- members[!is.na(Sustainability_experience) & !is.na(International)]
experts_no_NA <- experts[!is.na(Sustainability_experience) & !is.na(International)]

prop <- c (
  members_no_NA[Sustainability_experience == "No" & International == "No", .N] / members_no_NA[Sustainability_experience == "No",.N],
  members_no_NA[Sustainability_experience == "No" & International == "Yes", .N] / members_no_NA[Sustainability_experience == "No",.N],
  experts_no_NA[International == "No", .N] / experts_no_NA[, .N],
  experts_no_NA[International == "Yes", .N] / experts_no_NA[, .N]
)
#prop <- c((members[!is.na(Sustainability_experience) & !is.na(International)][Sustainability_experience == "N" & International == "Yes", .N]/members[!is.na(Sustainability_experience) & !is.na(International),.N]),
#           (members[!is.na(Sustainability_experience) & !is.na(International)][Sustainability_experience == "N" & International == "No", .N]/members[!is.na(Sustainability_experience) & !is.na(International),.N]), 
 #         (experts[International == "Yes", .N]/experts[,.N]), (experts[International == "No", .N]/experts[,.N]))

SE <- c("No", "No", "Yes", "Yes")

inter <- c("No", "Yes", "No", "Yes")

dt_prop <- data.table(Proportion = prop, Sustainability_Experience = SE, International = inter)

ggplot(dt_prop, aes(x = Sustainability_Experience, fill = International, weight= Proportion)) + geom_bar() + ylab("Proportion") + xlab("Has sustainability experience?") + scale_fill_manual(values = c("#fa766e", "#00bf7d")) + theme(legend.position = "bottom")

# Z test to check if the difference is significant
q1 <- members_no_NA[Sustainability_experience == "No" & International == "Yes", .N]
q2 <- members_no_NA[Sustainability_experience == "Yes" & International == "Yes", .N]

n1 <- members_no_NA[Sustainability_experience == "No", .N]
n2 <- members_no_NA[Sustainability_experience == "Yes", .N]

p1 <- q1 / n1
p2 <- q2 / n2
p_pooled <- (q1 + q2) / (n1 + n2)

z <- (p1 - p2) / sqrt((p_pooled * (1 - p_pooled))/ n1 + (p_pooled * (1 - p_pooled))/n2)
p_value <- 2 * pnorm(z, lower.tail = T)
#prop.test(x = c(q1,q2), n = c(n1,n2))
```

## Count of Structural approaches
```{r, fig.width= 10}
count <- c(sum(companies$Sustainability_Committee), sum(companies$Alleged_Expert), sum(companies$Sustainability_Expert), sum(companies$Trainning), sum(companies$Task_of_existing_committee))

approaches <- c("Sustainability Committee", "Alleged Expert", "Sustainability Expert", "Training", "Task of Existing Committee")

dt_approaches <- data.table(Approach = approaches, Count = count)

ggplot(dt_approaches, aes(weight = Count, fill = Approach)) + geom_bar(aes(x = Approach), position = position_dodge(10)) + xlab("Structural approach") + theme(axis.text = element_text(size = 12), legend.position = "none") + geom_text(aes(label=..weight.., y = Count, x = Approach),position = position_dodge(1), vjust=-0.5)

```

# Distribution of industries
```{r, fig.height=6}
industry_names<- unique(companies[,Industry])
counts <- rep(NA,26)
sustainability_counts <- rep(NA, 26)

for(i in c(1:26)) {
  count <- 0
  sustainability_count <- 0
  for (j in c(1:nrow(companies))){
      if (companies[j, Industry] == industry_names[i]){
        count = count + 1
        if(companies[j, Sustainability_Experience] == "Yes"){
          sustainability_count = sustainability_count + 1
        }
      }
  }
  counts[i] <- count
  sustainability_counts[i] <- sustainability_count
}

industries <- data.table(Name = industry_names, Count = counts, Yes = sustainability_counts, No = counts - sustainability_counts)
setorder(industries, Count, Yes)
industries_1 <- industries[1:5]
industries_2 <- industries[6:10]
industries_3 <- industries[11:15]
industries_4 <- industries[16:20]
industries_5 <- industries[21:26]

industries <- melt(industries, id.vars = "Name", measure.vars = c("Yes", "No"), variable.name = "Sustainability_Experience", value.name = "Value")
industries_1 <- melt(industries_1, id.vars = "Name", measure.vars = c("Yes", "No"), variable.name = "Sustainability_Experience", value.name = "Value")
industries_2 <- melt(industries_2, id.vars = "Name", measure.vars = c("Yes", "No"), variable.name = "Sustainability_Experience", value.name = "Value")
industries_3 <- melt(industries_3, id.vars = "Name", measure.vars = c("Yes", "No"), variable.name = "Sustainability_Experience", value.name = "Value")
industries_4 <- melt(industries_4, id.vars = "Name", measure.vars = c("Yes", "No"), variable.name = "Sustainability_Experience", value.name = "Value")
industries_5 <- melt(industries_5, id.vars = "Name", measure.vars = c("Yes", "No"), variable.name = "Sustainability_Experience", value.name = "Value")

ggplot(industries, aes(x = reorder(Name, Value), fill = Sustainability_Experience, y = Value)) + geom_bar(position = "stack", stat = "identity") + coord_flip() + labs(fill = "Sustainabiliy Experience") + theme(axis.title.x = element_blank(), axis.title.y = element_blank()) + scale_fill_manual(values = c("#00bf7d", "#fa766e")) + theme(legend.position = "bottom", legend.title = element_text(size = 12))

```


# Committee participation
```{r}
com1 <- unique(members[, str_trim(Committee_1)])
com2 <- unique(members[, str_trim(Committee_2)])
com3 <- unique(members[, str_trim(Committee_3)])
com4 <- unique(members[, str_trim(Committee_4)])
com5 <- unique(members[, str_trim(Committee_5)])
com6 <- unique(members[, str_trim(Committee_6)])
com7 <- unique(members[, str_trim(Committee_7)])
committee_names <- unique(c(com1, com2, com3, com4, com5, com6, com7))
committee_names <- committee_names[!is.na(committee_names) & committee_names != ""]

members[is.na(Committee_2), Committee_2 := "None"]
members[is.na(Committee_3), Committee_3 := "None"]
members[is.na(Committee_4), Committee_4 := "None"]
members[is.na(Committee_5), Committee_5 := "None"]
members[is.na(Committee_6), Committee_6 := "None"]
members[is.na(Committee_7), Committee_7 := "None"]
members[is.na(Sustainability_experience), Sustainability_experience := "ND"]

counts <- rep(NA,48)
sustainability_counts <- rep(NA,48)
for(i in c(1:48)) {
  count <- 0
  sustainability_count <- 0
  for(j in c(1:nrow(members))) {
    if(members[j, Committee_1] == committee_names[i]) {
      count = count + 1
      if(members[j, Sustainability_experience] == "Yes"){
        sustainability_count <- sustainability_count + 1
      }
    if(members[j, Committee_2] == committee_names[i]) {
      count = count + 1
      if(members[j, Sustainability_experience] == "Yes"){
        sustainability_count <- sustainability_count + 1
      }
    }
    if(members[j, Committee_3] == committee_names[i]) {
      count = count + 1
      if(members[j, Sustainability_experience] == "Yes"){
        sustainability_count <- sustainability_count + 1
      }
    }
    if(members[j, Committee_4] == committee_names[i]) {
      count = count + 1
      if(members[j, Sustainability_experience] == "Yes"){
        sustainability_count <- sustainability_count + 1
      }
    }
    if(members[j, Committee_5] == committee_names[i]) {
      count = count + 1
      if(members[j, Sustainability_experience] == "Yes"){
        sustainability_count <- sustainability_count + 1
      }
    }
    if(members[j, Committee_6] == committee_names[i]) {
      count = count + 1
      if(members[j, Sustainability_experience] == "Yes"){
        sustainability_count <- sustainability_count + 1
      }
    }
    if(members[j, Committee_7] == committee_names[i]) {
      count = count + 1
      if(members[j, Sustainability_experience] == "Yes"){
        sustainability_count <- sustainability_count + 1
      }
    }
    }
  }
  counts[i] <- count
  sustainability_counts[i] <- sustainability_count
  
}

committee_dt <- data.table(Name = committee_names, Members = counts, Sustainability_Experience = sustainability_counts)

setorder(committee_dt, cols = - "Sustainability_Experience")
committee_dt[Sustainability_Experience > 0]

```